Ecological Modeling HW3

### 2018-03-29 1062_class/eco_model/HW/C3/HW2.rmd
update

@@

    return 0;
}
```
Download [source1.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W2/source1.c){target="_blank"}

@@

@@

    printf("Your age is %d and your height is %.1f cm.\n", age, height);

    return 0;
}
```
Download [source2.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W2/source2.c){target="_blank"}

>>>>

> How old are you? (output)
>
> 23 ⏎ (input)
>
> You are 23 years old. (output)

@@

    return 0;
}
```
Download [source1.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C3/source1.c){target="_blank"}

@@

> Please input your age and height (cm). (output)
>
> 23 ⏎ (input)
> 
> 172.3 ⏎ (input)
>
> Your age is 23 and your height is 172.3 cm. (output)

@@

    printf("Your age is %d and your height is %.1lf cm.\n", age, height);

    return 0;
}
```
Download [source2.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C3/source2.c){target="_blank"}

### 2018-03-29 1062_class/eco_model/HW/C4/HW3.rmd
update

@@

```
Download [Q1.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W3/Q1.c){target="_blank"}

@@

@@

    return 0;
}
```
Download [Q2.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/W3/Q2.c){target="_blank"}

>>>>

> Please input the bottom length of a triangle (integer). (output)
> 
> 3 ⏎ (input)
> 
> Please input the height of the triangle (integer). (output)
> 
> 4 ⏎ (input)
> 
> The area of the triangle is 6.00. (output)

@@

```
Download [Q1.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C4/Q1.c){target="_blank"}

@@

> Please input your height (cm) and weight (kg). (output)
>
> 172.3 ⏎ (input)
>
> 65.0 ⏎ (input)
>
> Your BMI is XXXX. (output)
>
> The standard BMI is assumed to be 24.0. (output)
>
> The difference with a standard weight is YYY kg. (output)

@@

    return 0;
}
```
Download [Q2.c](https://minhaskamal.github.io/DownGit/#/home?url=https://github.com/liao961120/local_depend/blob/master/1062_class/eco_model/HW/C4/Q2.c){target="_blank"}
